---
title: "package_setup"
author: "joshmschmidt"
date: "03/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### Setting up this package
follow steps here: https://happygitwithr.com/new-github-first.html

```{r, eval=FALSE}
library(devtools)
library(usethis)
library(roxygen2)
library(ggplot2)
library(data.table)
use_description()
use_namespace()
  usethis::use_package("roxygen2")
usethis::use_package("data.table")
usethis::use_package("Rcpp")
usethis::use_package("pacman")
usethis::use_package("parallel")
usethis::use_package("NMOF")
usethis::use_package("DescTools")
usethis::use_package("Matrix")
usethis::use_package("RcppArmadillo")
usethis::use_package("RcppEigen")
devtools::document()
usethis::use_rcpp()
usethis::use_rcpp_eigen()
usethis::use_rcpp_armadillo()
usethis::use_rcpp_eigen()

```


then add R folder to project directory, manually in R file finder

```{bash Generate msms example data, eval=FALSE}
# mu = 1e-8; rho = mu; locuslength = 20e6;Ne = 1e4; s = 0.01; additive;
# samples 30 ingroup, 1 outgroup chromosomes = 31.
msms="/Users/joshua_schmidt/msms/lib/msms.jar"
out="${HOME}/Documents/acad/acad_projects/phisweepr/inst/extdata"
java -Xmx6G -jar ${msms} 31 1 -t 8000 -r 8000 20000001 -I 2 30 1 0.01 -SAA 200 -SaA 100  -Sc 0 2 0 0 0 -SF 0 -N 10000 -seed 101010 -Smark -Sp 0.5 -oFP 0.00000000 > ${out}/msms.selection.outgroup.txt

discoal="/Users/joshua_schmidt/Documents/acad/acad_projects/selection.statistics/projectBins/discoal/discoal" 
${discoal} 31 1 1000000 -t 400 -r 400 -p 2 30 1 -ed 0.05 0 1 -ws 0.00 -a 200 -x 0.5 -c 0.7 -i 4 > ${out}/discoal.selection.outgroup.txt

discoal="/Users/joshua_schmidt/Documents/acad/acad_projects/selection.statistics/projectBins/discoal/discoal" 
${discoal} 31 1 1000000 -t 400 -r 400 -p 2 30 1 -ed 0.05 0 1 -ws 0.00 -a 200 -x 0.5 -c 0.7 -i 4 > ${out}/discoal.neutral.outgroup.txt

``` 

```{r read in and process a basic msms selection scan, eval=FALSE}
ms.data <- "/Users/joshua_schmidt/Documents/acad/acad_projects/phisweepr/inst/extdata/msms.selection.outgroup.txt"
discoal.data <- "/Users/joshua_schmidt/Documents/acad/acad_projects/phisweepr/inst/extdata/discoal.selection.outgroup.txt"
#example.data <- get.ms.output(ms.file = ms.data)
example.data <- get.simulated.data(discoal.data, "discoal")
usethis::use_data(example.data, name="simData",internal = TRUE,overwrite = TRUE)
```

### NOTE *****
Check makevars file - if it has openmp, it will fuck up on mac, as clang does not support it.

```{r sfs object from genome object}
library(devtools)
library(usethis)
library(roxygen2)
library(data.table)
library(ggplot2)
library(viridis)
library(cowplot)
# genome object is example.data
# idea is to have a toplevel function 'calculate_SFSs', which returns a list object with 1-d SFS, 2-d SFS, empirical and theoretocal 
# have to estimate the mutation rate. using pi.
#load_all()
source('R/sfs_functions.R')
Rcpp::sourceCpp('src/rcpp_sfs_functions.cpp')
Rcpp::sourceCpp('src/xtensorArrays.cpp')

one_dimensional_sfs <- get_sfs(example.data$genotypes, fixed_derived = FALSE)
mutation_rate <- theta_from_pi(one_dimensional_sfs[["derived_allele_counts"]],nSam = example.data$sample.size, locusLength = example.data$locusLength)
```


##### What are the different options we an have
estimate the SFS form the data, or assume the neutral equilibrium model.  
whether to use all sites or only polymorphic sites (and within that the use of fixed derived)  


```{r Vy + Kim generation of equilibirum SFS, fig.height= 5, fig.width= 15}
load("data/example.data.rda")
dataObject <- example.data
example.data[["derived_allele_counts"]] <- Matrix::diff(dataObject$genotypes@p)
n1Min <- round(dataObject$sample.size*0.25)
n1Max <- round(dataObject$sample.size*0.75)
binomial.coeffs <- CbTable(dataObject$sample.size)
subP <- subPop_freqSpec(binomial.coeffs,dataObject$sample.size)
pHomo <- calc_pHomo(binomial.coeffs,dataObject$sample.size,n1Max,n1Min)
## can get the same thing as.....
subP_2 <- Matrix::Matrix(do.call(rbind,lapply(0:dataObject$sample.size,function(x) {sfs <- numeric(dataObject$sample.size+1); if(x > 1) {sfs[1:x] <-  1/(0:(x-1))}; sfs[1] <- 0; sfs })),sparse = TRUE)
# these are very close in values, down to 2e-7 at WORST.
unlist(lapply(1:31, function(x) all.equal(subP[x,],subP_2[x,],tolerance = 2e-7)))


## empirical conditional SFS
# i have two functions. one returns a single DT, the other a list of matrices.
#obs.cond.2d.sfs <- get_two_dimensionalSFSDT(dataObject = dataObject,n1Min = 1,n1Max = 30,monomorphic = FALSE,fixedDerived = FALSE)
obs.cond.2d.sfsL <- get_two_dimensionalSFSlist(dataObject = dataObject,n1Min = 1,n1Max = 30,monomorphic = FALSE,fixedDerived = FALSE)
#sfsCube <- listMatricesToArmaCube(obs.cond.2d.sfsL,n1Min,n1Max)
nkMatrix <- getSfs_perN_from_two_dimensionalSFSlist(two_dimensionalSFSlist = obs.cond.2d.sfsL,monomorphic = FALSE,fixedDerived = FALSE)




## assumed equilibirum sfs
neutralExpSfsCube <- standardNeutralJointSFSArmaCube(CbTable = binomial.coeffs,pHomo = pHomo, n1Min = n1Min, n1Max = n1Max, nSam = dataObject$sample.size,theta = mutation_rate, monomorphic = FALSE,fixedDerived = FALSE)
neutralExpSfsCube[,,8]


```

```{r convert obs cube slice to data.table and plot}
cols <- viridis(10)
# can convert a slice to a long formatDT
obsSFSlong <- sfsMatrixToLongDT(sfsMatrix =  sfsCube[,,8],
                              n1 = 15,
                              nSam = dataObject$sample.size)
pObs <- ggplot(obsSFSlong, aes(k1, k2)) +
  geom_tile(aes(fill = log10(frequency))) +
  scale_fill_gradientn(colours = cols) + coord_equal()
```

```{r convert exp cube slice to data.table and plot}
expSFSlong <- sfsMatrixToLongDT(sfsMatrix = neutralExpSfsCube[,,8],
                              n1 = 15,
                              nSam = dataObject$sample.size)
pExp <- ggplot(expSFSlong, aes(k1, k2)) +
  geom_tile(aes(fill = log10(frequency))) +
  scale_fill_gradientn(colours = cols) + coord_equal()
```

```{r find residuals and plot}
# residuals
setkey(obsSFSlong,n1,k1,k2)
setkey(expSFSlong,n1,k1,k2) 
comSFSlong <- obsSFSlong[expSFSlong]
comSFSlong[,residual:=frequency-i.frequency]
pRes <- ggplot(comSFSlong, aes(k1, k2)) +
  geom_tile(aes(fill = residual)) +
  scale_fill_gradientn(colours = cols) + coord_equal()

plot_grid(pExp, pObs, pRes,nrow = 1,labels = c('expected', 'observed', 'residuals: obs-exp'),align = "hv")
```



```{r expand.grid in r}
n1 <- 22
n2 = 30 - 22
k1 <- 0:n1
k2 <- 0:n2
l <- length(k1) * length(k2)
a <- array(dim=c(l,2))
for(j in seq_along(k2)){
  
}
```

